\section{Contributions of group members}

\subsection{Matt}

\begin{itemize}
    \item Wrote and ran our initial experiments, training on the GSM8K and MATH datasets in an unordered fashion.
    \item Ran a majority of training runs (both unsorted data and sorted/curriculum structured data) as well as numerous inference runs on the MATH test set for final results.
    \item Compiled training histories to create all training graphs for the report.
    \item Hosted the GitHub repository and Overleaf projects for our code and report, respectively. 
\end{itemize}

\subsection{Aishwarya}
\begin{itemize}
    \item Wrote and ran the training loop for the unordered combined datasets 
    \item Implemented and ran numerous inference runs on the MATH test set for results 
    \item Implemented the evaluation loop for evaluation using math-verify
\end{itemize}
\subsection{Takuto}

\begin{itemize}
    \item Wrote batch processing script to automatically evaluate difficulty levels of the GSM8K dataset using OpenAI's GPT-4o mini model.
    \item Created notebook pipeline for fine-tuning difficulty ordered GSM8K training data.
    \item Ran training runs for ordered GSM8K models.
\end{itemize}

\subsection{Hung}
\begin{itemize}
    \item Wrote and conducted experiments, finetuning the baseline model on GSM8K and MATH datasets in a sorted order. 
    \item Evaluating the test sets
    \item Ran training runs, and inference runs on the MATH test set to generate comparable results to provide model accuracy.
\end{itemize}

% List what each member of the group contributed to this project here. For example: 
% \begin{itemize}
%     \item member 1: did data collection / processing and lots of writing
%     \item member 2: built and trained models
%     \item member 3: error analysis and annotations
% \end{itemize}

% \textbf{If you would like to privately share more information about the workload division that may have caused extenuating circumstances (e.g., a member of the group was unreachable and did no work), please send a detailed note to the instructors GMail account. We will take these notes into account when assigning individual grades.}
